Should I Fuzz my Inputs or Improve my Test Suite? Lessons from Differential Testing Runtime Engines.

### 2018-06-28 paper/paper.tex
add seeds discussion and grammar-based fuzzers section (wip)

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cyclic icons denote repetition--the leftmost cyclic icon
indicates that each file in the input list will be analyzed in
separate and the rightmost icon indicates that a single file will be
processed multiple times in fuzzing mode. The bug-finding process
takes on input JS files from regression test suites of various JS
engines. Table~\ref{tab:test-suites} shows the JS sources we mined
from online repositories of various open-source engines. Overall, we
found a total of \Fix{XX} JS files.

\begin{table}[h]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Fix{use path in the repo}}
  \begin{tabular}{ccc}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    \Fix{duktape} & - & - \\
    \Fix{jerryjs} & - & - \\
    \Fix{jsi} & - & - \\
    \Fix{tiny} & - & - \\
    \Fix{mozilla} & - & - \\
    v8.test.benchmarks.data & - & - \\
    webkit.jstests.es6 & - & - \\
    webkit.jstests.microbenchmarks & - & - \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

\subsection{Constants.}~We used the following engines in
this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
(WebKit)~\Fix{cite}. We selected these engines based on
popularity~\Fix{cite}. Considering fuzzing tools, we used
representatives of the most popular approaches to fuzzing. For
random-based fuzzing we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

@@

>>>>

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cyclic icons denote repetition--the leftmost cyclic icon
indicates that each file in the input list will be analyzed in
separate and the rightmost icon indicates that a single file will be
processed multiple times in fuzzing mode. The bug-finding process
takes on input JS files from regression test suites of various JS
engines.

\Igor{
\subsection{Populating seed files.}~This section describes 
how we found valid javascript files based on 
existing sources on the open-source repositories.
Originally, we mined JS engines repositories that we 
support (ie. V8, SpiderMonkey, Chakra and JavascriptCore) and 
we found a total of \Fix{XX} files of regression suites and 
benchmarks testing involving javascript files.
Latelly, we need to increase our input seeds through existing
open-sources projects that involves javascript engines.
We mined repositories from GitHub based on these requirements:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item The tests should be plug-and-play and/or easy integration.
\end{itemize}

We wrote a query to mine these repositories on GitHub
\CodeIn{\url{https://api.github.com/search/repositories?q=javascript-engine&sort=stars&order=desc}}\Fix{wip}
and we follow the requirements ignoring invalid projects.
\Fix{discuss wip}

Table~\ref{tab:test-suites} shows the JS sources we mined
from online repositories of various open-source engines. Overall, we
found a total of \Fix{30K} JS files.
}
\Igor{
\begin{itemize}
  \item discuss about changes in seeds for run in our infraestructure (wip)
  \item discuss about generating new files via fuzzers grammar-based (wip)
  \item discuss about mutation fuzzers (wip)
\end{itemize}
}

\begin{table}[h]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Fix{use path in the repo}}
  \begin{tabular}{ccc}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    \Fix{duktape} & - & 997 \\
    \Fix{jerryjs} & - & 1.803 \\
    \Fix{jsi} & - & 99 \\
    \Fix{tiny} & - & 44 \\
    \Fix{mozilla} & - & - \\
    v8.test.benchmarks.data & - & 64 \\
    webkit.jstests.es6 & - & 605 \\
    webkit.jstests.microbenchmarks & - & 426 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}\\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

\subsection{Constants.}~We used the following engines in
this study: Microsoft's Chakra~\cite{chakra2018repo}, Google's v8~\cite{v82018repo},
Mozilla's SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
(WebKit)~\cite{jsc2018repo}. We selected these engines based on
popularity~\Fix{cite}. Considering fuzzing tools, we used
representatives of the most popular approaches to fuzzing. For
random-based fuzzing we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

@@

\Igor{
\subsection{Grammar-based Fuzzers}
Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).
Our infrastructure supports any grammar fuzzer with a few adjusts. However, 
we try to integrate several grammar-based fuzzers, for example 
Grammarinator~\footnote{https://github.com/renatahodovan/grammarinator}, QuickFuzz~\cite{grieco2016quickfuzz}
and \Fix{others fuzzers} to generate new JavaScript files based on grammar, but 
after several runs it was observed that this approach was ineffective
due the amount of invalid files and/or files without discrepancies. For example, if we ran 
Grammarinator to generate 1K JS files ten times with a random seed generation, we obtained
\Fix{XX\%} of valid files. Checking in our environment almost \Fix{XX\%}
are js files that shows undefined variables and due the differential testing in our environment
all engines will raise a SyntaxError and this approach was not relevant to our experiment.
}
